\documentclass[11pt, letterpaper]{article}

\usepackage[right = 25mm, left = 25mm, top = 25mm, bottom = 25mm]{geometry}
\usepackage[final, nopatch = footnote]{microtype}
\usepackage{parskip}
\usepackage{xcolor}

\setlength{\parskip}{\baselineskip}

\pagestyle{empty}

\begin{document}

\begin{flushright}
    \color{gray}
    \textbf{David L칩pez del Pino}

    \vspace{-\baselineskip}
    \textsl{29004 M치laga}

    \vspace{-\baselineskip}
    \textsl{Spain}


    \vspace{-\baselineskip}
    \textsl{+34 622 23 23 87}

    \vspace{-\baselineskip}
    \textsl{lopezdelpinodavid@gmail.com}

\end{flushright}

\textbf{Betsson Group} \hfill July 19, 2025

\vspace{-\baselineskip}
\textsl{Spain}

Dear Betsson Group's recruitment team:

I am writing to express my interest in the Data Engineer position. As a recent graduate in Mathematics from the University of M치laga and passionate about technology, I am motivated to participate in projects related to the development of programs that require problem-solving and analytical-thinking skills. 

Throughout my degree in Mathematics, I have learned to use different technologies and programming languages to implement numerical methods and to solve abstract mathematical problems. The programming languages I have mastered have been Scala, Haskell, Java, C++, R and Python, especially the latter. In the last three years, I have worked with Python on a regular basis to develop projects related to the degree, and I have learned to write code in a clean, efficient and organised way to implement complex algorithms and analyse results rigorously. Programming in a language as versatile as Python has given me a strong interest in expanding my knowledge in the field of data engineering, so I am willing to learn to work with any new technologies that could be needed for this position.

I consider myself to be an organised, responsible, energetic and determined person, with excellent learning capacity and communication skills. I am also highly curious and creative and I like to acquire new knowledge in my free time to develop personal projects. 

I am very motivated to start building a career in data engineering and I think this position in Betsson Group is a perfect opportunity to do so.

Thank you in advance for considering my application. 

Best regards,

\vspace{-\baselineskip}
David L칩pez del Pino

\end{document}